---
title: "Validation SoccerNet 1.0.0"
output: pdf_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
library(readxl)
library(dplyr)
library(tidyverse)
library(socR)
library(gtsummary)
library(gt)
library(kableExtra)
source('read_coder_file.R', local = TRUE)
source('rank.R', local = TRUE)
source('summarize_df_weighted.R', local = TRUE)
source('pivot_data_longer.R', local = TRUE)
source('faceted_comp_plot_wt.R', local = TRUE)
```

# Data Inputs
## Coder
```{r coder datasets, include = FALSE}
usr_coder <- read_coder_file('/Users/orszagl2/Documents/socR/usr_coder.csv')
lymph_coder <- read_coder_file("/Users/orszagl2/Documents/socR/asia_lymph_coder.csv")
atp_coder <- read_coder_file("/Users/orszagl2/Documents/socR/atp500_coder.csv")
```

## No Crosswalk
```{r no xwalk datasets, include = FALSE}
usr_no_crosswalk <- read_excel("/Users/orszagl2/Documents/socR/model_final/usr_no_xw.xlsx")
lymph_no_crosswalk <- read_excel("/Users/orszagl2/Documents/socR/model_final/lymph_no_xw.xlsx")
atp_no_crosswalk <- read_excel("/Users/orszagl2/Documents/socR/model_final/atp_no_xw.xlsx")
```

## Crosswalk
```{r xwalk datasets, include = FALSE}
usr_crosswalk <- read_excel("/Users/orszagl2/Documents/socR/model_final/usr_xw.xlsx")
lymph_crosswalk <- read_excel("/Users/orszagl2/Documents/socR/model_final/lymph_xw.xlsx")
atp_crosswalk <- read_excel("/Users/orszagl2/Documents/socR/model_final/atp_xw.xlsx")
```

# Agreement
```{r calculating agreement, include= FALSE}
# USR
usr_cmp <- rank(usr_no_crosswalk, usr_coder)
usr_cmp_crosswalk <- rank(usr_crosswalk, usr_coder)
# ATP
atp_cmp <- rank(atp_no_crosswalk, atp_coder)
atp_cmp_crosswalk <- rank(atp_crosswalk, atp_coder)
# Lymph
lymph_cmp <- rank(lymph_no_crosswalk, lymph_coder)
lymph_cmp_crosswalk <- rank(lymph_crosswalk, lymph_coder)
```

# Full Datasets (X-walk Joined with Non-Xwalk & # of scores)
## Crosswalks
```{r read in xwalks, include = FALSE}
xwalk_lymph = read.csv('/Users/orszagl2/Documents/socR/crosswalk files/isco1988_soc2010.csv')
xwalk_lymph = xwalk(xwalk_lymph)
xwalk_usr = read.csv('/Users/orszagl2/Documents/socR/crosswalk files/soc1980_soc2010.csv')
xwalk_usr = xwalk(xwalk_usr)
xwalk_atp = read.csv('/Users/orszagl2/Documents/socR/crosswalk files/noc2011_soc2010_via_soc2018.csv')
xwalk_atp = xwalk(xwalk_atp)
```

# Functions Needed
```{r to levels, include = FALSE}
to_2d <- to_level(soc2010_all,soc2d)
to_3d <- to_level(soc2010_all,soc3d)
to_5d <- to_level(soc2010_all,soc5d)
```

```{r replacements, include = FALSE}
replace_with_to_5d <- function(df) {
  # Loop through each column name
  df <- df %>%
    mutate(across(starts_with("soc2010"), ~ to_5d(.)))
  return(df)
}

replace_with_to_2d <- function(df) {
  # Loop through each column name
  df <- df %>%
    mutate(across(starts_with("soc2010"), ~ to_2d(.)))
  
  return(df)
}
replace_with_to_3d <- function(df) {
  # Loop through each column name
  df <- df %>%
    mutate(across(starts_with("soc2010"), ~ to_3d(.)))
  
  return(df)
}
```

# Graph
```{r set up longer df, include = FALSE}
df_summary1 = data.frame(
  interval = levels(cut(seq(0, 1, length.out = 100), 
                        breaks = seq(0, 1, length.out = 21), 
                        include.lowest = TRUE)))
```

```{r set up shorter df, include = FALSE}
df_summary2 = data.frame(
  interval = levels(cut(seq(0, 1, length.out = 100), 
                        breaks = seq(0, 1, length.out = 11), 
                        include.lowest = TRUE)))
```

```{r labels & fill in summary df, include = FALSE}
df_summary1$usr_no_x <- summarize_df_weighted(usr_cmp, 21, "usr_no_x", "usr_no_x_pct")
df_summary1$usr_x <- summarize_df_weighted(usr_cmp_crosswalk, 21, "usr_x", "usr_x_pct")
df_summary2$atp_no_x <- summarize_df_weighted(atp_cmp, 11, "atp_no_x", "atp_no_x_pct")
df_summary2$atp_x <- summarize_df_weighted(atp_cmp_crosswalk, 11, "atp_x", "atp_x_pct")
df_summary2$lymph_no_x <- summarize_df_weighted(lymph_cmp, 11, "lymph_no_x", "lymph_no_x_pct")
df_summary2$lymph_x <- summarize_df_weighted(lymph_cmp_crosswalk, 11, "lymph_x", "lymph_x_pct")
```

```{r fix interval labels, include = FALSE}
df_summary1$start_value = as.numeric(sub("\\((.+),.+\\]", "\\1", as.character(df_summary1$interval)))
df_summary2$start_value = as.numeric(sub("\\((.+),.+\\]", "\\1", as.character(df_summary2$interval)))
df_summary1$start_value = replace_na(df_summary1$start_value, 0)
df_summary2$start_value = replace_na(df_summary2$start_value, 0)
```

```{r full summary & graph, warning = FALSE, echo = FALSE}
df_summary3 = full_join(df_summary2, select(df_summary1, - interval), by = "start_value")
df_long <- pivot_data_long(df_summary3)
faceted_comp_plot_wt(df_long)
```

# Table 1
## Set Up Dataframe
```{r empty df, include = FALSE}
result_df = data.frame(row.names = c("usr_no_x", "usr_x", "atp_no_x", "atp_x", "lymph_no_x", "lymph_x"))
```

## 6 Digit Agreement
### USR
```{r usr 6 dig, include = FALSE}
usr_cmp <- rank(usr_no_crosswalk, usr_coder)
result_df[1,1] = usr_cmp %>%
  summarise(pctAg = mean(rank == 1)) %>%
  pull(pctAg)
usr_cmp_crosswalk <- rank(usr_crosswalk, usr_coder)
result_df[2,1] = usr_cmp_crosswalk %>%
  summarise(pctAg = mean(rank == 1)) %>%
  pull(pctAg)
```

### ATP
```{r atp 6 dig, include = FALSE}
atp_cmp <- rank(atp_no_crosswalk, atp_coder)
result_df[3,1] = atp_cmp %>%
  summarise(pctAg = mean(rank == 1)) %>%
  pull(pctAg)
atp_cmp_crosswalk <- rank(atp_crosswalk, atp_coder)
result_df[4,1] = atp_cmp_crosswalk %>%
  summarise(pctAg = mean(rank == 1)) %>%
  pull(pctAg)
```

### Lymph
```{r lymph 6 dig, include = FALSE}
lymph_cmp <- rank(lymph_no_crosswalk, lymph_coder)
result_df[5,1] = lymph_cmp %>%
  summarise(pctAg = mean(rank == 1)) %>%
  pull(pctAg)
lymph_cmp_crosswalk <- rank(lymph_crosswalk, lymph_coder)
result_df[6,1] = lymph_cmp_crosswalk %>%
  summarise(pctAg = mean(rank == 1)) %>%
  pull(pctAg)
```

## 5 Digit Agreement
### USR
```{r recode coding df usr 5dig, include = FALSE}
usr_coder_recode <- data.frame(
  soc2010_coder = unlist(usr_coder$soc2010_coder),
  row_id = rep(usr_coder$row_id, each = 3) # Ensure each `row_id` repeats 3 times
)
usr_coder_recode$dig5 <- to_5d(usr_coder_recode$soc2010_coder)
usr_coder5 = usr_coder
usr_coder5 <- usr_coder_recode %>%
  group_by(row_id) %>%
  summarise(soc2010_coder = list(dig5), .groups = "drop") %>%
  right_join(select(usr_coder, -soc2010_coder), by = "row_id")
```

```{r usr replacement, include = FALSE}
usr_crosswalk5 = replace_with_to_5d(usr_crosswalk)
usr_no_crosswalk5 = replace_with_to_5d(usr_no_crosswalk)
```

```{r usr table 5 dig, include = FALSE}
usr_cmp5 <- rank(usr_no_crosswalk5, usr_coder5)
result_df[1,2] = usr_cmp5 %>%
  summarise(pctAg = mean(rank == 1)) %>%
  pull(pctAg)
usr_cmp_crosswalk5 <- rank(usr_crosswalk5, usr_coder5)
result_df[2,2] = usr_cmp_crosswalk5 %>%
  summarise(pctAg = mean(rank == 1)) %>%
  pull(pctAg)
```

### ATP
```{r recode coding df atp 5 dig, include = FALSE}
atp_coder_recode <- data.frame(
  soc2010_coder = unlist(atp_coder$soc2010_coder),
  row_id = rep(atp_coder$row_id, each = 3) # Ensure each `row_id` repeats 3 times
)
atp_coder_recode$dig5 <- to_5d(atp_coder_recode$soc2010_coder)
atp_coder5 = atp_coder
atp_coder5 <- atp_coder_recode %>%
  group_by(row_id) %>%
  summarise(soc2010_coder = list(dig5), .groups = "drop") %>%
  right_join(select(atp_coder, -soc2010_coder), by = "row_id")
```

```{r atp replacement, include = FALSE}
atp_crosswalk5 = replace_with_to_5d(atp_crosswalk)
atp_no_crosswalk5 = replace_with_to_5d(atp_no_crosswalk)
```

```{r atp table 5 dig, include = FALSE}
atp_cmp5 <- rank(atp_no_crosswalk5, atp_coder5)
result_df[3,2] = atp_cmp5 %>%
  summarise(pctAg = mean(rank == 1)) %>%
  pull(pctAg)
atp_cmp_crosswalk5 <- rank(atp_crosswalk5, atp_coder5)
result_df[4,2] = atp_cmp_crosswalk5 %>%
  summarise(pctAg = mean(rank == 1)) %>%
  pull(pctAg)
```

### Lymph
```{r recode coding df lymph 5 dig, include = FALSE}
lymph_coder_recode <- data.frame(
  soc2010_coder = unlist(lymph_coder$soc2010_coder),
  row_id = rep(lymph_coder$row_id, each = 3) # Ensure each `row_id` repeats 3 times
)
lymph_coder_recode$dig5 <- to_5d(lymph_coder_recode$soc2010_coder)
lymph_coder5 <- lymph_coder_recode %>%
  group_by(row_id) %>%
  summarise(soc2010_coder = list(dig5), .groups = "drop") %>%
  right_join(select(lymph_coder, -soc2010_coder), by = "row_id")
```

```{r lymph replacement, include = FALSE}
lymph_crosswalk5 = replace_with_to_5d(lymph_crosswalk)
lymph_no_crosswalk5 = replace_with_to_5d(lymph_no_crosswalk)
```

```{r lymph table 5 dig, include = FALSE}
lymph_cmp5 <- rank(lymph_no_crosswalk5, lymph_coder5)
result_df[5,2] = lymph_cmp5 %>%
  summarise(pctAg = mean(rank == 1)) %>%
  pull(pctAg)
lymph_cmp_crosswalk5 <- rank(lymph_crosswalk5, lymph_coder5)
result_df[6,2] = lymph_cmp_crosswalk5 %>%
  summarise(pctAg = mean(rank == 1)) %>%
  pull(pctAg)
```

### USR
```{r recode coding usr 3 dig, include = FALSE}
usr_coder_recode$dig3 <- to_3d(usr_coder_recode$soc2010_coder)
usr_coder3 <- usr_coder_recode %>%
  group_by(row_id) %>%
  summarise(soc2010_coder = list(dig3), .groups = "drop") %>%
  right_join(select(usr_coder, -soc2010_coder), by = "row_id")
```

```{r usr replacement 3 dig, include = FALSE}
usr_crosswalk3 = replace_with_to_3d(usr_crosswalk)
usr_no_crosswalk3 = replace_with_to_3d(usr_no_crosswalk)
```

```{r usr table 3 dig, include = FALSE}
usr_cmp3 <- rank(usr_no_crosswalk3, usr_coder3)
result_df[1,3] = usr_cmp3 %>%
  summarise(pctAg = mean(rank == 1)) %>%
  pull(pctAg)
usr_cmp_crosswalk3 <- rank(usr_crosswalk3, usr_coder3)
result_df[2,3] = usr_cmp_crosswalk3 %>%
  summarise(pctAg = mean(rank == 1)) %>%
  pull(pctAg)
```

### ATP
```{r recode coding atp 3 dig, include = FALSE}
atp_coder_recode$dig3 <- to_3d(atp_coder_recode$soc2010_coder)
atp_coder3 = atp_coder
atp_coder3 <- atp_coder_recode %>%
  group_by(row_id) %>%
  summarise(soc2010_coder = list(dig3), .groups = "drop") %>%
  right_join(select(atp_coder, -soc2010_coder), by = "row_id")
```

```{r atp replacement 3 dig, include = FALSE}
atp_crosswalk3 = replace_with_to_3d(atp_crosswalk)
atp_no_crosswalk3 = replace_with_to_3d(atp_no_crosswalk)
```

```{r atp table 3 dig, include = FALSE}
atp_cmp3 <- rank(atp_no_crosswalk3, atp_coder3)
result_df[3,3] = atp_cmp3 %>%
  summarise(pctAg = mean(rank == 1)) %>%
  pull(pctAg)
atp_cmp_crosswalk3 <- rank(atp_crosswalk3, atp_coder3)
result_df[4,3] = atp_cmp_crosswalk3 %>%
  summarise(pctAg = mean(rank == 1)) %>%
  pull(pctAg)
```

### Lymph
```{r recode coding lymph 3 dig, include = FALSE}
lymph_coder_recode$dig3 <- to_3d(lymph_coder_recode$soc2010_coder)
lymph_coder3 = lymph_coder
lymph_coder3 <- lymph_coder_recode %>%
  group_by(row_id) %>%
  summarise(soc2010_coder = list(dig3), .groups = "drop") %>%
  right_join(select(lymph_coder, -soc2010_coder), by = "row_id")
```

```{r lymph replacement 3 dig, include = FALSE}
lymph_crosswalk3 = replace_with_to_3d(lymph_crosswalk)
lymph_no_crosswalk3 = replace_with_to_3d(lymph_no_crosswalk)
```

```{r lymph table 3 dig, include = FALSE}
lymph_cmp3 <- rank(lymph_no_crosswalk3, lymph_coder3)
result_df[5,3] = lymph_cmp3 %>%
  summarise(pctAg = mean(rank == 1)) %>%
  pull(pctAg)
lymph_cmp_crosswalk3 <- rank(lymph_crosswalk3, lymph_coder3)
result_df[6,3] = lymph_cmp_crosswalk3 %>%
  summarise(pctAg = mean(rank == 1)) %>%
  pull(pctAg)
```


## 2 Digit Agreement
### USR
```{r recode coding usr 2 dig, include = FALSE}
usr_coder_recode$dig2 <- to_2d(usr_coder_recode$soc2010_coder)
usr_coder2 = atp_coder
usr_coder2 <- usr_coder_recode %>%
  group_by(row_id) %>%
  summarise(soc2010_coder = list(dig2), .groups = "drop") %>%
  right_join(select(usr_coder, -soc2010_coder), by = "row_id")
```

```{r usr replacement 2 dig, include = FALSE}
usr_crosswalk2 = replace_with_to_2d(usr_crosswalk)
usr_no_crosswalk2 = replace_with_to_2d(usr_no_crosswalk)
```

```{r usr table 2 dig, include = FALSE}
usr_cmp2 <- rank(usr_no_crosswalk2, usr_coder2)
result_df[1,4] = usr_cmp2 %>%
  summarise(pctAg = mean(rank == 1)) %>%
  pull(pctAg)
usr_cmp_crosswalk2 <- rank(usr_crosswalk2, usr_coder2)
result_df[2,4] = usr_cmp_crosswalk2 %>%
  summarise(pctAg = mean(rank == 1)) %>%
  pull(pctAg)
```

### ATP
```{r recode coding atp 2 dig, include = FALSE}
atp_coder_recode$dig2 <- to_2d(atp_coder_recode$soc2010_coder)
atp_coder2 = atp_coder
atp_coder2 <- atp_coder_recode %>%
  group_by(row_id) %>%
  summarise(soc2010_coder = list(dig2), .groups = "drop") %>%
  right_join(select(atp_coder, -soc2010_coder), by = "row_id")
```

```{r atp replacement 2 dig, include = FALSE}
atp_crosswalk2 = replace_with_to_2d(atp_crosswalk)
atp_no_crosswalk2 = replace_with_to_2d(atp_no_crosswalk)
```

```{r atp table 2 dig, include = FALSE}
atp_cmp2 <- rank(atp_no_crosswalk2, atp_coder2)
result_df[3,4] = atp_cmp2 %>%
  summarise(pctAg = mean(rank == 1)) %>%
  pull(pctAg)
atp_cmp_crosswalk2 <- rank(atp_crosswalk2, atp_coder2)
result_df[4,4] = atp_cmp_crosswalk2 %>%
  summarise(pctAg = mean(rank == 1)) %>%
  pull(pctAg)
```

### Lymph
```{r recode coding lymph 2 dig, include = FALSE}
lymph_coder_recode$dig2 <- to_2d(lymph_coder_recode$soc2010_coder)
lymph_coder2 = atp_coder
lymph_coder2 <- lymph_coder_recode %>%
  group_by(row_id) %>%
  summarise(soc2010_coder = list(dig2), .groups = "drop") %>%
  right_join(select(lymph_coder, -soc2010_coder), by = "row_id")
```

```{r lymph replacement 2 dig, include = FALSE}
lymph_crosswalk2 = replace_with_to_2d(lymph_crosswalk)
lymph_no_crosswalk2 = replace_with_to_2d(lymph_no_crosswalk)
```

```{r lymph table 2 dig, include = FALSE}
lymph_cmp2 <- rank(lymph_no_crosswalk2, lymph_coder2)
result_df[5,4] = lymph_cmp2 %>%
  summarise(pctAg = mean(rank == 1)) %>%
  pull(pctAg)
lymph_cmp_crosswalk2 <- rank(lymph_crosswalk2, lymph_coder2)
result_df[6,4] = lymph_cmp_crosswalk2 %>%
  summarise(pctAg = mean(rank == 1)) %>%
  pull(pctAg)
```

## Ties
### USR
```{r usr ties, include = FALSE}
result_df[1,5] = usr_no_crosswalk%>%
  summarise(pct = mean(score_1-score_2<10^-6)) %>%
  pull(pct)
result_df[2,5] = usr_crosswalk%>%
  summarise(pct = mean(score_1-score_2<10^-6)) %>%
  pull(pct)
```

### ATP
```{r atp ties, include = FALSE}
result_df[3,5] = atp_no_crosswalk%>%
  summarise(pct = mean(score_1-score_2<10^-6)) %>%
  pull(pct)
result_df[4,5] = atp_crosswalk%>%
  summarise(pct = mean(score_1-score_2<10^-6)) %>%
  pull(pct)
```

### Lymph
```{r lymph ties, include = FALSE}
result_df[5,5] = lymph_no_crosswalk%>%
  summarise(pct = mean(score_1-score_2<10^-6)) %>%
  pull(pct)
result_df[6,5] = lymph_crosswalk%>%
  summarise(pct = mean(score_1-score_2<10^-6)) %>%
  pull(pct)
```

# Thresholds
```{r}
ties_1 = usr_no_crosswalk%>%
  summarise(pct_6 = mean(score_1-score_2<10^-6),
            pct_5 = mean(score_1-score_2<10^-5),
            pct_4 = mean(score_1-score_2<10^-4),
            pct_3 = mean(score_1-score_2<10^-3))%>%
  mutate(study = "usr_no_xw")

ties_2 = usr_crosswalk%>%
  summarise(pct_6 = mean(score_1-score_2<10^-6),
            pct_5 = mean(score_1-score_2<10^-5),
            pct_4 = mean(score_1-score_2<10^-4),
            pct_3 = mean(score_1-score_2<10^-3))%>%
  mutate(study = "usr_xw")

ties_3 = lymph_no_crosswalk%>%
  summarise(pct_6 = mean(score_1-score_2<10^-6),
            pct_5 = mean(score_1-score_2<10^-5),
            pct_4 = mean(score_1-score_2<10^-4),
            pct_3 = mean(score_1-score_2<10^-3))%>%
  mutate(study = "lymph_no_xw")

ties_4 = lymph_crosswalk%>%
  summarise(pct_6 = mean(score_1-score_2<10^-6),
            pct_5 = mean(score_1-score_2<10^-5),
            pct_4 = mean(score_1-score_2<10^-4),
            pct_3 = mean(score_1-score_2<10^-3))%>%
  mutate(study = "lymph_xw")

ties_5 = atp_no_crosswalk%>%
  summarise(pct_6 = mean(score_1-score_2<10^-6),
            pct_5 = mean(score_1-score_2<10^-5),
            pct_4 = mean(score_1-score_2<10^-4),
            pct_3 = mean(score_1-score_2<10^-3))%>%
  mutate(study = "atp_no_xw")

ties_6 = atp_crosswalk%>%
  summarise(pct_6 = mean(score_1-score_2<10^-6),
            pct_5 = mean(score_1-score_2<10^-5),
            pct_4 = mean(score_1-score_2<10^-4),
            pct_3 = mean(score_1-score_2<10^-3))%>%
  mutate(study = "atp_xw")

ties = rbind(ties_1, ties_2, ties_3, ties_4, ties_5, ties_6)
ties = ties[,c(5, 1, 2,3,4)]
ties[] <- lapply(ties, function(x) {
  if (is.numeric(x)) round(x * 100, 2) else x
})
ties %>%kable(col.names = c("Study", "10^-6 Threshold", "10^-5 Threshold", "10^-4 Threshold", "10^-3 Threshold"))
```


## Medians
### USR
```{r usr medians, include = FALSE}
result_df[1,6] = usr_no_crosswalk%>%
  summarise(med = median(score_1)) %>%
  pull(med)
result_df[2,6] = usr_crosswalk%>%
  summarise(med = median(score_1)) %>%
  pull(med)
```

### ATP
```{r atp median, include = FALSE}
result_df[3,6] = atp_no_crosswalk%>%
  summarise(med = median(score_1)) %>%
  pull(med)
result_df[4,6] = atp_crosswalk%>%
  summarise(med = median(score_1)) %>%
  pull(med)
```

### Lymph
```{r lymph medians, include = FALSE}
result_df[5,6] = lymph_no_crosswalk%>%
  summarise(med = median(score_1)) %>%
  pull(med)
result_df[6,6] = lymph_crosswalk%>%
  summarise(med = median(score_1)) %>%
  pull(med)
```

## IQRs
### USR
```{r usr iqrs, include = FALSE}
result_df[1,7] = usr_no_crosswalk%>%
  summarise(q1 = list(quantile(score_1, probs = 0.25))) %>%
  pull(q1)
result_df[1,8] = usr_no_crosswalk%>%
  summarise(q3 = list(quantile(score_1, probs = 0.75))) %>%
  pull(q3)
result_df[2,7] = usr_crosswalk%>%
  summarise(q1 = list(quantile(score_1, probs = 0.25))) %>%
  pull(q1)
result_df[2,8] = usr_crosswalk%>%
  summarise(q3 = list(quantile(score_1, probs = 0.75))) %>%
  pull(q3)
```

### ATP
```{r atp iqrs, include = FALSE}
result_df[3,7] = atp_no_crosswalk%>%
  summarise(q1 = list(quantile(score_1, probs = 0.25))) %>%
  pull(q1)
result_df[3,8] = atp_no_crosswalk%>%
  summarise(q3 = list(quantile(score_1, probs = 0.75))) %>%
  pull(q3)
result_df[4,7] = atp_crosswalk%>%
  summarise(q1 = list(quantile(score_1, probs = 0.25))) %>%
  pull(q1)
result_df[4,8] = atp_crosswalk%>%
  summarise(q3 = list(quantile(score_1, probs = 0.75))) %>%
  pull(q3)
```

### Lymph
```{r lymph iqrs, include = FALSE}
result_df[5,7] = lymph_no_crosswalk%>%
  summarise(q1 = list(quantile(score_1, probs = 0.25))) %>%
  pull(q1)
result_df[5,8] = lymph_no_crosswalk%>%
  summarise(q3 = list(quantile(score_1, probs = 0.75))) %>%
  pull(q3)
result_df[6,7] = lymph_crosswalk%>%
  summarise(q1 = list(quantile(score_1, probs = 0.25))) %>%
  pull(q1)
result_df[6,8] = lymph_crosswalk%>%
  summarise(q3 = list(quantile(score_1, probs = 0.75))) %>%
  pull(q3)
```

```{r name columns, include = FALSE}
colnames(result_df) = c("6dig", "5dig", "3dig", "2dig", "tie", "median_score", "q1", "q3")
```

```{r rounded table, include = FALSE}
result_df2 <- result_df %>%
  mutate(
    median_score = round(median_score, 2),
    q1 = round(q1, 2),
    q3 = round(q3, 2),
    combined = paste0(median_score, " (", q1, "-", q3, ")")
  )
```

```{r reorg table, include = FALSE}
result_df = result_df2[, c("2dig", "3dig", "5dig", "6dig", "combined")]
colnames(result_df) = c("2-Digit", "3-Digit", "5-Digit", "6-Digit", "Median (IQR)")
```


# Table
```{r rename rows, include = FALSE}
result_df <- result_df %>%
  tibble::rownames_to_column("rownames")
result_df$Group = c("US Renal", "US Renal", "ATP", "ATP", "Asia Lymph", "Asia Lymph")
```

```{r rename row spanners, include = FALSE}
result_df$rownames= c("Without Crosswalk", "With Crosswalk","Without Crosswalk", "With Crosswalk","Without Crosswalk", "With Crosswalk")
```

```{r create table, width = 10, height = 8, echo = FALSE}
result_df %>%
  gt(rowname_col = "rownames", groupname_col = "Group", row_group_as_column = TRUE) %>%
  fmt_percent(
    columns = c("6-Digit", "5-Digit", "3-Digit", "2-Digit"),
    decimals = 2  # Round to 2 decimal places
  ) %>%
  tab_spanner(
    label = "Percent agreement by SOC hierarchical levels",
    columns = c("6-Digit", "5-Digit", "3-Digit", "2-Digit")
  ) %>%
  tab_options(
    table.font.size = "80%",            # Reduce font size to 80% of default
    data_row.padding = px(3),          # Reduce padding between rows
    row_group.padding = px(3),         # Reduce padding for row groups
    table.width = pct(100)             # Ensure the table width stretches to fit
  )
```

# Ranks Dataframe
```{r create dataframe, include = FALSE}
ranks_df = data.frame(1,2,3,4,5,6,7,8,9,10,11)
```

```{r usr no xwalk, include = FALSE}
ranks_df[1,] <- usr_cmp %>%
  summarize(
    !!!setNames(
      lapply(1:max(.$rank, na.rm = TRUE), function(i) mean(.$rank <= i, na.rm = TRUE)),
      paste0("pct_", 1:max(.$rank, na.rm = TRUE))
    )
  )
```

```{r usr xwalk, include = FALSE}
ranks_df[2,] <- usr_cmp_crosswalk %>%
  summarize(
    !!!setNames(
      lapply(1:max(.$rank, na.rm = TRUE), function(i) mean(.$rank <= i, na.rm = TRUE)),
      paste0("pct_", 1:max(.$rank, na.rm = TRUE))
    )
  )
```

```{r atp no xwalk, include = FALSE}
ranks_df[3,] <- atp_cmp %>%
  summarize(
    !!!setNames(
      lapply(1:max(.$rank, na.rm = TRUE), function(i) mean(.$rank <= i, na.rm = TRUE)),
      paste0("pct_", 1:max(.$rank, na.rm = TRUE))
    )
  )
```

```{r atp xwalk, include = FALSE}
ranks_df[4,] <- atp_cmp_crosswalk %>%
  summarize(
    !!!setNames(
      lapply(1:max(.$rank, na.rm = TRUE), function(i) mean(.$rank <= i, na.rm = TRUE)),
      paste0("pct_", 1:max(.$rank, na.rm = TRUE))
    )
  )
```

```{r lymph no xwalk, include = FALSE}
ranks_df[5,] <- lymph_cmp %>%
  summarize(
    !!!setNames(
      lapply(1:max(.$rank, na.rm = TRUE), function(i) mean(.$rank <= i, na.rm = TRUE)),
      paste0("pct_", 1:max(.$rank, na.rm = TRUE))
    )
  )
```

```{r lymph xwalk, include = FALSE}
ranks_df[6,] <- lymph_cmp_crosswalk %>%
  summarize(
    !!!setNames(
      lapply(1:max(.$rank, na.rm = TRUE), function(i) mean(.$rank <= i, na.rm = TRUE)),
      paste0("pct_", 1:max(.$rank, na.rm = TRUE))
    )
  )
```

```{r reorganize table, include = FALSE}
rownames(ranks_df) = c("USR without Crosswalk", "USR with Crosswalk", "ATP without Crosswalk", "ATP with Crosswalk", "Asia Lymph without Crosswalk", "Asia Lymph with Crosswalk")
```

```{r pivot df, include = FALSE}
ranks_df <- ranks_df %>%
  rownames_to_column(var = "study") # "study" will hold the old row names

long_df <- ranks_df %>%
  pivot_longer(
    cols = starts_with("X"),     # Select percentage columns
    names_to = "pct_rank",          # New column for the rank
    values_to = "cumulative_pct"    # New column for the cumulative percentage
  ) %>%
  mutate(
    pct_rank = as.numeric(gsub("X", "", pct_rank)) # Convert rank names to numeric
  )
```

## Plot
```{r plot, echo = FALSE}
ggplot(long_df, aes(x = pct_rank, y = cumulative_pct, color = study, group = study)) +
  geom_line(size = 1) +
  geom_point(size = 2) +
  labs(
    x = "Rank of expert SOC",
    y = "Cumulative proportion of jobs",
    title = "Cumulative Percentages by Rank",
    color = "Study"
  ) +
  scale_x_continuous(breaks = 1:11) +
  scale_y_continuous(limits = c(0,1))+
  theme_minimal()
```

```{r create rank dataframe}
all_ranks <- tibble(rank = sort(unique(c(
  usr_cmp$rank,
  usr_cmp_crosswalk$rank,
  atp_cmp$rank,
  atp_cmp_crosswalk$rank,
  lymph_cmp$rank,
  lymph_cmp_crosswalk$rank
))))

# Step 2: Create full count tables with all ranks
usr_noxw_r <- all_ranks %>%
  left_join(usr_cmp %>% count(rank), by = "rank") %>%
  replace_na(list(n = 0))

usr_xw_r <- all_ranks %>%
  left_join(usr_cmp_crosswalk %>% count(rank), by = "rank") %>%
  replace_na(list(n = 0))

atp_noxw_r <- all_ranks %>%
  left_join(atp_cmp %>% count(rank), by = "rank") %>%
  replace_na(list(n = 0))

atp_xw_r <- all_ranks %>%
  left_join(atp_cmp_crosswalk %>% count(rank), by = "rank") %>%
  replace_na(list(n = 0))

lymph_noxw_r <- all_ranks %>%
  left_join(lymph_cmp %>% count(rank), by = "rank") %>%
  replace_na(list(n = 0))

lymph_xw_r <- all_ranks %>%
  left_join(lymph_cmp_crosswalk %>% count(rank), by = "rank") %>%
  replace_na(list(n = 0))

# Step 3: Bind into a final dataframe
rank_num_df <- tibble(
  rank = all_ranks$rank,
  usr_noxw = usr_noxw_r$n,
  usr_xw = usr_xw_r$n,
  atp_noxw = atp_noxw_r$n,
  atp_xw = atp_xw_r$n,
  lymph_noxw = lymph_noxw_r$n,
  lymph_xw = lymph_xw_r$n
)

```

```{r}
ranks_num_long = pivot_longer(rank_num_df, cols = -rank, names_to = "study")
ranks_num_long = separate_wider_delim(ranks_num_long, cols = study, delim =  "_", names = c("study_name", "XW"))
ranks_num_long$study_name = gsub("usr", "US Renal", ranks_num_long$study_name)
ranks_num_long$study_name = gsub("atp", "ATP", ranks_num_long$study_name)
ranks_num_long$study_name = gsub("lymph", "Asia Lymph", ranks_num_long$study_name)
ranks_num_long$XW = gsub("noxw", "Without Crosswalk", ranks_num_long$XW)
ranks_num_long$XW = gsub("xw", "With Crosswalk", ranks_num_long$XW)
```

```{r}
ggplot(ranks_num_long, aes(x= rank, y = value))+
  geom_bar(stat = 'identity')+
  facet_grid(study_name~XW, scales = "free")+
  theme_bw()+
  scale_x_continuous(breaks = c(1:11), labels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11+"))+
  labs(x = "Rank", y = "Number of Jobs")
```

```{r}
ggsave("faceted_rank_bars.png", plot = last_plot(), dpi = 300)
```


# Score Changes
```{r score change dataframes}
usr_full = usr_cmp_crosswalk%>%
  select(Id, hi_score)%>%
  inner_join(select(usr_cmp, c(Id, hi_score)), by = "Id", suffix = c("_xw", "_no_xw"))%>%
  mutate(diff = hi_score_xw - hi_score_no_xw)

lymph_full = lymph_cmp_crosswalk%>%
  select(Id, hi_score)%>%
  inner_join(select(lymph_cmp, c(Id, hi_score)), by = "Id", suffix = c("_xw", "_no_xw"))%>%
  mutate(diff = hi_score_xw - hi_score_no_xw)

atp_full = atp_cmp_crosswalk%>%
  select(Id, hi_score)%>%
  inner_join(select(atp_cmp, c(Id, hi_score)), by = "Id", suffix = c("_xw", "_no_xw"))%>%
  mutate(diff = hi_score_xw - hi_score_no_xw)
```

```{r histograms}
ggplot(usr_full, aes(x = diff))+
  geom_histogram(binwidth = .05, fill = "cornflowerblue")+
  xlim(-1, 1)+
  labs(x = "Score 1 Difference (Crosswalk - No Crosswalk)",
       title = "USR Score Differences with & Without Crosswalk")+
  theme_minimal()

ggplot(atp_full, aes(x = diff))+
  geom_histogram(binwidth = .05, fill = "pink2")+
  xlim(-1, 1)+
  labs(x = "Score 1 Difference (Crosswalk - No Crosswalk)",
       title = "ATP Score Differences with & Without Crosswalk")+
  theme_minimal()

ggplot(lymph_full, aes(x = diff))+
  geom_histogram(binwidth = .05, fill = "green4")+
  xlim(-1, 1)+
  labs(x = "Score 1 Difference (Crosswalk - No Crosswalk)",
       title = "Asia Lymph Score Differences with & Without Crosswalk")+
  theme_minimal()
```
```{r scatter plots with and without crosswalk}
ggplot(usr_full, aes(x = hi_score_no_xw, y = hi_score_xw))+
  geom_point()+
  xlim(0, 1)+
  labs(x = "Score 1 Without Crosswalk",
       y = "Score 1 With Crosswalk",
       title = "USR Scores with/without Crosswalk")+
  theme_minimal()

ggplot(lymph_full, aes(x = hi_score_no_xw, y = hi_score_xw))+
  geom_point()+
  xlim(0, 1)+
  labs(x = "Score 1 Without Crosswalk",
       y = "Score 1 With Crosswalk",
       title = "Asia Lymph Scores with/without Crosswalk")+
  theme_minimal()

ggplot(atp_full, aes(x = hi_score_no_xw, y = hi_score_xw))+
  geom_point()+
  xlim(0, 1)+
  labs(x = "Score 1 Without Crosswalk",
       y = "Score 1 With Crosswalk",
       title = "ATP Scores with/without Crosswalk")+
  theme_minimal()
```
# Rank == 1 Comparison
```{r ranked dataframes}
usr_rank = usr_cmp_crosswalk%>%
  select(Id, rank)%>%
  inner_join(select(usr_cmp, c(Id, rank)), by = "Id", suffix = c("_xw", "_no_xw"))%>%
  mutate(match_noxw = ifelse(rank_no_xw == 1, 1, 0),
         match_xw = ifelse(rank_xw == 1, 1, 0))

atp_rank = atp_cmp_crosswalk%>%
  select(Id, rank)%>%
  inner_join(select(atp_cmp, c(Id, rank)), by = "Id", suffix = c("_xw", "_no_xw"))%>%
  mutate(match_noxw = ifelse(rank_no_xw == 1, 1, 0),
         match_xw = ifelse(rank_xw == 1, 1, 0))

lymph_rank = lymph_cmp_crosswalk%>%
  select(Id, rank)%>%
  inner_join(select(lymph_cmp, c(Id, rank)), by = "Id", suffix = c("_xw", "_no_xw"))%>%
  mutate(match_noxw = ifelse(rank_no_xw == 1, 1, 0),
         match_xw = ifelse(rank_xw == 1, 1, 0))
```

```{r}
usr_rank%>%tbl_cross(row = match_noxw, col = match_xw)%>% modify_caption("USR Agreement with & without XW")
atp_rank%>%tbl_cross(row = match_noxw, col = match_xw)%>% modify_caption("ATP Agreement with & without XW")
lymph_rank%>%tbl_cross(row = match_noxw, col = match_xw)%>% modify_caption("Asia Lymph Agreement with & without XW")
```

```{r}
kappa2(usr_rank[, 4:5])
kappa2(atp_rank[, 4:5])
kappa2(lymph_rank[, 4:5])
```

```{r}
cor.test(usr_full$hi_score_no_xw, usr_full$hi_score_xw, method = "spearman")
cor.test(atp_full$hi_score_no_xw, atp_full$hi_score_xw, method = "spearman")
cor.test(lymph_full$hi_score_no_xw, lymph_full$hi_score_xw, method = "spearman")
```

