---
title: "Tables & Figures"
output:
  pdf_document: default
  html_document: default
date: "2025-01-10"
---

```{r setup, include=FALSE}
library(readxl)
library(dplyr)
library(tidyverse)
library(socR)
library(gtsummary)
library(gt)
library(kableExtra)
```

```{r}
to_2d <- to_level(soc2010_all,soc2d)
to_3d <- to_level(soc2010_all,soc3d)
to_5d <- to_level(soc2010_all,soc5d)
```

```{r}
rank <- function(soccer, coder, nomatch = 11) {
  soccer %>% 
    right_join(select(coder, Id, soc2010_coder, row_id), by = "Id") %>%
    mutate(
      # Directly handle soc2010_coder and soc2010_soccer without nesting/unlisting
      rank = map2_int(soc2010_coder, soc2010_soccer, \(x, y) {
        ranks <- match(x, y, nomatch = nomatch)
        if (length(ranks) == 0) nomatch else min(ranks, na.rm = TRUE) # Pick the minimum rank
      }),
      hi_score = map_dbl(score, \(x) x[1])) %>%
    arrange(Id)
}
```

# Data Inputs
## Coder
```{r}
usr_coder <- read_csv("/Users/orszagl2/Documents/socR/usr_coder.csv",show_col_types = FALSE) %>%
  filter(is_valid_6digit_soc2010(soc2010_1)) %>%
  mutate(
    Id=paste0(str_pad(Id,5,"left","0")),
    soc2010_coder = pmap(list(soc2010_1, soc2010_2, soc2010_3), ~ c(..1, ..2, ..3)),
    row_id = row_number())
```

```{r}
lymph_coder <- read_csv("/Users/orszagl2/Documents/socR/asia_lymph_coder.csv",show_col_types = FALSE) %>%
  filter(is_valid_6digit_soc2010(soc2010_1)) %>%
  mutate(
    Id=paste0(str_pad(Id,5,"left","0")),
    soc2010_coder = pmap(list(soc2010_1, soc2010_2, soc2010_3), ~ c(..1, ..2, ..3)),
    row_id = row_number())
```

```{r}
atp_coder <- read_csv("/Users/orszagl2/Documents/socR/atp500_coder.csv",show_col_types = FALSE) %>%
  filter(is_valid_6digit_soc2010(soc2010_1)) %>%
  mutate(
    Id=paste0(str_pad(Id,5,"left","0")),
    soc2010_coder = pmap(list(soc2010_1, soc2010_2, soc2010_3), ~ c(..1, ..2, ..3)),
    row_id = row_number())
```

## No Crosswalk
```{r}
usr_no_crosswalk <- read_excel("/Users/orszagl2/Documents/socR/usr_no_crosswalk.xlsx")
atp_no_crosswalk <- read_excel("/Users/orszagl2/Documents/socR/atp_no_crosswalk.xlsx")
lymph_no_crosswalk <- read_excel("/Users/orszagl2/Documents/socR/asia_lymph_no_crosswalk.xlsx")
```

## Crosswalk
```{r}
usr_crosswalk <- read_excel("/Users/orszagl2/Documents/socR/usr_crosswalk.xlsx")
atp_crosswalk <- read_excel("/Users/orszagl2/Documents/socR/atp_crosswalk.xlsx")
lymph_crosswalk <- read_excel("/Users/orszagl2/Documents/socR/asia_lymph_crosswalk.xlsx")
```

## Soccer 2.0
```{r}
usr_soc2 = read.csv('/Users/orszagl2/Documents/socR/soc2.0 files/usr_results.csv')
atp_soc2 = read.csv('/Users/orszagl2/Documents/socR/soc2.0 files/atp_results.csv')
lymph_soc2 = read.csv('/Users/orszagl2/Documents/socR/soc2.0 files/lymph_results.csv')
```

# Table 1
## Set Up Dataframe
```{r}
result_df = data.frame(row.names = c("usr_no_x", "usr_x", "atp_no_x", "atp_x", "lymph_no_x", "lymph_x"))
```

## 6 Digit Agreement
### USR
```{r}
usr_cmp <- rank(usr_no_crosswalk, usr_coder)
result_df[1,1] = usr_cmp %>%
  summarise(pctAg = mean(rank == 1)) %>%
  pull(pctAg)
usr_cmp_crosswalk <- rank(usr_crosswalk, usr_coder)
result_df[2,1] = usr_cmp_crosswalk %>%
  summarise(pctAg = mean(rank == 1)) %>%
  pull(pctAg)
usr_cmp_soc2 = rank(usr_soc2, usr_coder)
```

### ATP
```{r}
atp_cmp <- rank(atp_no_crosswalk, atp_coder)
result_df[3,1] = atp_cmp %>%
  summarise(pctAg = mean(rank == 1)) %>%
  pull(pctAg)
atp_cmp_crosswalk <- rank(atp_crosswalk, atp_coder)
result_df[4,1] = atp_cmp_crosswalk %>%
  summarise(pctAg = mean(rank == 1)) %>%
  pull(pctAg)
atp_cmp_soc2 = rank(atp_soc2, atp_coder)
```

### Lymph
```{r}
lymph_cmp <- rank(lymph_no_crosswalk, lymph_coder)
result_df[5,1] = lymph_cmp %>%
  summarise(pctAg = mean(rank == 1)) %>%
  pull(pctAg)
lymph_cmp_crosswalk <- rank(lymph_crosswalk, lymph_coder)
result_df[6,1] = lymph_cmp_crosswalk %>%
  summarise(pctAg = mean(rank == 1)) %>%
  pull(pctAg)
lymph_cmp_soc2 = rank(lymph_soc2, lymph_coder)
```

## 5 Digit Agreement
```{r}
replace_with_to_5d <- function(df) {
  # Loop through each column name
  df <- df %>%
    mutate(across(starts_with("soc2010"), ~ to_5d(.)))
  return(df)
}
```

### USR
```{r}
usr_coder_recode <- data.frame(
  soc2010_coder = unlist(usr_coder$soc2010_coder),
  row_id = rep(usr_coder$row_id, each = 3) # Ensure each `row_id` repeats 3 times
)
usr_coder_recode$dig5 <- to_5d(usr_coder_recode$soc2010_coder)
usr_coder5 = usr_coder
usr_coder5 <- usr_coder_recode %>%
  group_by(row_id) %>%
  summarise(soc2010_coder = list(dig5), .groups = "drop") %>%
  right_join(select(usr_coder, -soc2010_coder), by = "row_id")
```

```{r}
usr_crosswalk5 = replace_with_to_5d(usr_crosswalk)
usr_no_crosswalk5 = replace_with_to_5d(usr_no_crosswalk)
```

```{r}
usr_cmp5 <- rank(usr_no_crosswalk5, usr_coder5)
result_df[1,2] = usr_cmp5 %>%
  summarise(pctAg = mean(rank == 1)) %>%
  pull(pctAg)
usr_cmp_crosswalk5 <- rank(usr_crosswalk5, usr_coder5)
result_df[2,2] = usr_cmp_crosswalk5 %>%
  summarise(pctAg = mean(rank == 1)) %>%
  pull(pctAg)
```

### ATP
```{r}
atp_coder_recode <- data.frame(
  soc2010_coder = unlist(atp_coder$soc2010_coder),
  row_id = rep(atp_coder$row_id, each = 3) # Ensure each `row_id` repeats 3 times
)
atp_coder_recode$dig5 <- to_5d(atp_coder_recode$soc2010_coder)
atp_coder5 = atp_coder
atp_coder5 <- atp_coder_recode %>%
  group_by(row_id) %>%
  summarise(soc2010_coder = list(dig5), .groups = "drop") %>%
  right_join(select(atp_coder, -soc2010_coder), by = "row_id")
```

```{r}
atp_crosswalk5 = replace_with_to_5d(atp_crosswalk)
atp_no_crosswalk5 = replace_with_to_5d(atp_no_crosswalk)
```

```{r}
atp_cmp5 <- rank(atp_no_crosswalk5, atp_coder5)
result_df[3,2] = atp_cmp5 %>%
  summarise(pctAg = mean(rank == 1)) %>%
  pull(pctAg)
atp_cmp_crosswalk5 <- rank(atp_crosswalk5, atp_coder5)
result_df[4,2] = atp_cmp_crosswalk5 %>%
  summarise(pctAg = mean(rank == 1)) %>%
  pull(pctAg)
```

### Lymph

```{r}
lymph_coder_recode <- data.frame(
  soc2010_coder = unlist(lymph_coder$soc2010_coder),
  row_id = rep(lymph_coder$row_id, each = 3) # Ensure each `row_id` repeats 3 times
)
lymph_coder_recode$dig5 <- to_5d(lymph_coder_recode$soc2010_coder)
lymph_coder5 <- lymph_coder_recode %>%
  group_by(row_id) %>%
  summarise(soc2010_coder = list(dig5), .groups = "drop") %>%
  right_join(select(lymph_coder, -soc2010_coder), by = "row_id")
```

```{r}
lymph_crosswalk5 = replace_with_to_5d(lymph_crosswalk)
lymph_no_crosswalk5 = replace_with_to_5d(lymph_no_crosswalk)
```

```{r}
lymph_cmp5 <- rank(lymph_no_crosswalk5, lymph_coder5)
result_df[5,2] = lymph_cmp5 %>%
  summarise(pctAg = mean(rank == 1)) %>%
  pull(pctAg)
lymph_cmp_crosswalk5 <- rank(lymph_crosswalk5, lymph_coder5)
result_df[6,2] = lymph_cmp_crosswalk5 %>%
  summarise(pctAg = mean(rank == 1)) %>%
  pull(pctAg)
```

## 3 Digit Agreement
```{r}
replace_with_to_3d <- function(df) {
  # Loop through each column name
  df <- df %>%
    mutate(across(starts_with("soc2010"), ~ to_3d(.)))
  
  return(df)
}
```

### USR
```{r}
usr_coder_recode$dig3 <- to_3d(usr_coder_recode$soc2010_coder)
usr_coder3 <- usr_coder_recode %>%
  group_by(row_id) %>%
  summarise(soc2010_coder = list(dig3), .groups = "drop") %>%
  right_join(select(usr_coder, -soc2010_coder), by = "row_id")
```

```{r}
usr_crosswalk3 = replace_with_to_3d(usr_crosswalk)
usr_no_crosswalk3 = replace_with_to_3d(usr_no_crosswalk)
```

```{r}
usr_cmp3 <- rank(usr_no_crosswalk3, usr_coder3)
result_df[1,3] = usr_cmp3 %>%
  summarise(pctAg = mean(rank == 1)) %>%
  pull(pctAg)
usr_cmp_crosswalk3 <- rank(usr_crosswalk3, usr_coder3)
result_df[2,3] = usr_cmp_crosswalk3 %>%
  summarise(pctAg = mean(rank == 1)) %>%
  pull(pctAg)
```

### ATP
```{r}
atp_coder_recode$dig3 <- to_3d(atp_coder_recode$soc2010_coder)
atp_coder3 = atp_coder
atp_coder3 <- atp_coder_recode %>%
  group_by(row_id) %>%
  summarise(soc2010_coder = list(dig3), .groups = "drop") %>%
  right_join(select(atp_coder, -soc2010_coder), by = "row_id")
```

```{r}
atp_crosswalk3 = replace_with_to_3d(atp_crosswalk)
atp_no_crosswalk3 = replace_with_to_3d(atp_no_crosswalk)
```

```{r}
atp_cmp3 <- rank(atp_no_crosswalk3, atp_coder3)
result_df[3,3] = atp_cmp3 %>%
  summarise(pctAg = mean(rank == 1)) %>%
  pull(pctAg)
atp_cmp_crosswalk3 <- rank(atp_crosswalk3, atp_coder3)
result_df[4,3] = atp_cmp_crosswalk3 %>%
  summarise(pctAg = mean(rank == 1)) %>%
  pull(pctAg)
```

### Lymph

```{r}
lymph_coder_recode$dig3 <- to_3d(lymph_coder_recode$soc2010_coder)
lymph_coder3 = lymph_coder
lymph_coder3 <- lymph_coder_recode %>%
  group_by(row_id) %>%
  summarise(soc2010_coder = list(dig3), .groups = "drop") %>%
  right_join(select(lymph_coder, -soc2010_coder), by = "row_id")
```

```{r}
lymph_crosswalk3 = replace_with_to_3d(lymph_crosswalk)
lymph_no_crosswalk3 = replace_with_to_3d(lymph_no_crosswalk)
```

```{r}
lymph_cmp3 <- rank(lymph_no_crosswalk3, lymph_coder3)
result_df[5,3] = lymph_cmp3 %>%
  summarise(pctAg = mean(rank == 1)) %>%
  pull(pctAg)
lymph_cmp_crosswalk3 <- rank(lymph_crosswalk3, lymph_coder3)
result_df[6,3] = lymph_cmp_crosswalk3 %>%
  summarise(pctAg = mean(rank == 1)) %>%
  pull(pctAg)
```


## 2 Digit Agreement
```{r}
replace_with_to_2d <- function(df) {
  # Loop through each column name
  df <- df %>%
    mutate(across(starts_with("soc2010"), ~ to_2d(.)))
  
  return(df)
}
```

### USR
```{r}
usr_coder_recode$dig2 <- to_2d(usr_coder_recode$soc2010_coder)
usr_coder2 = atp_coder
usr_coder2 <- usr_coder_recode %>%
  group_by(row_id) %>%
  summarise(soc2010_coder = list(dig2), .groups = "drop") %>%
  right_join(select(usr_coder, -soc2010_coder), by = "row_id")
```

```{r}
usr_crosswalk2 = replace_with_to_2d(usr_crosswalk)
usr_no_crosswalk2 = replace_with_to_2d(usr_no_crosswalk)
```

```{r}
usr_cmp2 <- rank(usr_no_crosswalk2, usr_coder2)
result_df[1,4] = usr_cmp2 %>%
  summarise(pctAg = mean(rank == 1)) %>%
  pull(pctAg)
usr_cmp_crosswalk2 <- rank(usr_crosswalk2, usr_coder2)
result_df[2,4] = usr_cmp_crosswalk2 %>%
  summarise(pctAg = mean(rank == 1)) %>%
  pull(pctAg)
```

### ATP
```{r}
atp_coder_recode$dig2 <- to_2d(atp_coder_recode$soc2010_coder)
atp_coder2 = atp_coder
atp_coder2 <- atp_coder_recode %>%
  group_by(row_id) %>%
  summarise(soc2010_coder = list(dig2), .groups = "drop") %>%
  right_join(select(atp_coder, -soc2010_coder), by = "row_id")
```

```{r}
atp_crosswalk2 = replace_with_to_2d(atp_crosswalk)
atp_no_crosswalk2 = replace_with_to_2d(atp_no_crosswalk)
```

```{r}
atp_cmp2 <- rank(atp_no_crosswalk2, atp_coder2)
result_df[3,4] = atp_cmp2 %>%
  summarise(pctAg = mean(rank == 1)) %>%
  pull(pctAg)
atp_cmp_crosswalk2 <- rank(atp_crosswalk2, atp_coder2)
result_df[4,4] = atp_cmp_crosswalk2 %>%
  summarise(pctAg = mean(rank == 1)) %>%
  pull(pctAg)
```

### Lymph

```{r}
lymph_coder_recode$dig2 <- to_2d(lymph_coder_recode$soc2010_coder)
lymph_coder2 = atp_coder
lymph_coder2 <- lymph_coder_recode %>%
  group_by(row_id) %>%
  summarise(soc2010_coder = list(dig2), .groups = "drop") %>%
  right_join(select(lymph_coder, -soc2010_coder), by = "row_id")
```

```{r}
lymph_crosswalk2 = replace_with_to_2d(lymph_crosswalk)
lymph_no_crosswalk2 = replace_with_to_2d(lymph_no_crosswalk)
```

```{r}
lymph_cmp2 <- rank(lymph_no_crosswalk2, lymph_coder2)
result_df[5,4] = lymph_cmp2 %>%
  summarise(pctAg = mean(rank == 1)) %>%
  pull(pctAg)
lymph_cmp_crosswalk2 <- rank(lymph_crosswalk2, lymph_coder2)
result_df[6,4] = lymph_cmp_crosswalk2 %>%
  summarise(pctAg = mean(rank == 1)) %>%
  pull(pctAg)
```

## Ties

### USR
```{r}
result_df[1,5] = usr_no_crosswalk%>%
  summarise(pct = mean(score_1-score_2<10^-6)) %>%
  pull(pct)
result_df[2,5] = usr_crosswalk%>%
  summarise(pct = mean(score_1-score_2<10^-6)) %>%
  pull(pct)
```

### ATP
```{r}
result_df[3,5] = atp_no_crosswalk%>%
  summarise(pct = mean(score_1-score_2<10^-6)) %>%
  pull(pct)
result_df[4,5] = atp_crosswalk%>%
  summarise(pct = mean(score_1-score_2<10^-6)) %>%
  pull(pct)
```

### Lymph
```{r}
result_df[5,5] = lymph_no_crosswalk%>%
  summarise(pct = mean(score_1-score_2<10^-6)) %>%
  pull(pct)
result_df[6,5] = lymph_crosswalk%>%
  summarise(pct = mean(score_1-score_2<10^-6)) %>%
  pull(pct)
```

## Medians

### USR
```{r}
result_df[1,6] = usr_no_crosswalk%>%
  summarise(med = median(score_1)) %>%
  pull(med)
result_df[2,6] = usr_crosswalk%>%
  summarise(med = median(score_1)) %>%
  pull(med)
```

### ATP
```{r}
result_df[3,6] = atp_no_crosswalk%>%
  summarise(med = median(score_1)) %>%
  pull(med)
result_df[4,6] = atp_crosswalk%>%
  summarise(med = median(score_1)) %>%
  pull(med)
```

### Lymph
```{r}
result_df[5,6] = lymph_no_crosswalk%>%
  summarise(med = median(score_1)) %>%
  pull(med)
result_df[6,6] = lymph_crosswalk%>%
  summarise(med = median(score_1)) %>%
  pull(med)
```

## IQRs

### USR
```{r}
result_df[1,7] = usr_no_crosswalk%>%
  summarise(q1 = list(quantile(score_1, probs = 0.25))) %>%
  pull(q1)
result_df[1,8] = usr_no_crosswalk%>%
  summarise(q3 = list(quantile(score_1, probs = 0.75))) %>%
  pull(q3)
result_df[2,7] = usr_crosswalk%>%
  summarise(q1 = list(quantile(score_1, probs = 0.25))) %>%
  pull(q1)
result_df[2,8] = usr_crosswalk%>%
  summarise(q3 = list(quantile(score_1, probs = 0.75))) %>%
  pull(q3)
```

### ATP
```{r}
result_df[3,7] = atp_no_crosswalk%>%
  summarise(q1 = list(quantile(score_1, probs = 0.25))) %>%
  pull(q1)
result_df[3,8] = atp_no_crosswalk%>%
  summarise(q3 = list(quantile(score_1, probs = 0.75))) %>%
  pull(q3)
result_df[4,7] = atp_crosswalk%>%
  summarise(q1 = list(quantile(score_1, probs = 0.25))) %>%
  pull(q1)
result_df[4,8] = atp_crosswalk%>%
  summarise(q3 = list(quantile(score_1, probs = 0.75))) %>%
  pull(q3)
```

### Lymph
```{r}
result_df[5,7] = lymph_no_crosswalk%>%
  summarise(q1 = list(quantile(score_1, probs = 0.25))) %>%
  pull(q1)
result_df[5,8] = lymph_no_crosswalk%>%
  summarise(q3 = list(quantile(score_1, probs = 0.75))) %>%
  pull(q3)
result_df[6,7] = lymph_crosswalk%>%
  summarise(q1 = list(quantile(score_1, probs = 0.25))) %>%
  pull(q1)
result_df[6,8] = lymph_crosswalk%>%
  summarise(q3 = list(quantile(score_1, probs = 0.75))) %>%
  pull(q3)
```

```{r}
colnames(result_df) = c("6dig", "5dig", "3dig", "2dig", "tie", "median_score", "q1", "q3")
```


```{r}
result_df2 <- result_df %>%
  mutate(
    median_score = round(median_score, 2),
    q1 = round(q1, 2),
    q3 = round(q3, 2),
    combined = paste0(median_score, " (", q1, "-", q3, ")")
  )
```

```{r}
result_df = result_df2[, c("2dig", "3dig", "5dig", "6dig", "tie", "combined")]
```


```{r}
colnames(result_df) = c("2-Digit", "3-Digit", "5-Digit", "6-Digit", "Tie", "Median (IQR)")
```

# Table
```{r}
result_df <- result_df %>%
  tibble::rownames_to_column("rownames")
result_df$Group = c("US Renal", "US Renal", "ATP", "ATP", "Asia Lymph", "Asia Lymph")
```

```{r}
result_df$rownames= c("Without Crosswalk", "With Crosswalk","Without Crosswalk", "With Crosswalk","Without Crosswalk", "With Crosswalk")
```

```{r, width = 10, height = 8}
result_df %>%
  gt(rowname_col = "rownames", groupname_col = "Group", row_group_as_column = TRUE) %>%
  fmt_percent(
    columns = c("6-Digit", "5-Digit", "3-Digit", "2-Digit", "Tie"),
    decimals = 2  # Round to 2 decimal places
  ) %>%
  tab_spanner(
    label = "Percent agreement by SOC hierarchical levels",
    columns = c("6-Digit", "5-Digit", "3-Digit", "2-Digit")
  ) %>%
  tab_options(
    table.font.size = "80%",            # Reduce font size to 80% of default
    data_row.padding = px(3),          # Reduce padding between rows
    row_group.padding = px(3),         # Reduce padding for row groups
    table.width = pct(100)             # Ensure the table width stretches to fit
  )
```

# Graph
```{r}
df_summary <- usr_cmp %>%
  mutate(
    interval = cut(hi_score, breaks = seq(0, 1, length.out = 21), include.lowest = TRUE) # Create intervals
  ) %>%
  group_by(interval) %>% # Group by interval
  summarize(usr_no_x = mean(rank == 1))
```

```{r}
df_summary$usr_x <- usr_cmp_crosswalk %>%
  mutate(
    interval = cut(hi_score, breaks = seq(0, 1, length.out = 21), include.lowest = TRUE) # Create intervals
  ) %>%
  group_by(interval) %>% # Group by interval
  summarize(usr_x = mean(rank == 1))%>%
  pull(usr_x)
```

```{r}
df_summary$atp_no_x <- atp_cmp %>%
  mutate(
    interval = cut(hi_score, breaks = seq(0, 1, length.out = 21), include.lowest = TRUE) # Create intervals
  ) %>%
  group_by(interval) %>% # Group by interval
  summarize(atp_no_x = mean(rank == 1))%>%
  pull(atp_no_x)
```

```{r}
df_summary$atp_x <- atp_cmp_crosswalk %>%
  mutate(
    interval = cut(hi_score, breaks = seq(0, 1, length.out = 21), include.lowest = TRUE) # Create intervals
  ) %>%
  group_by(interval) %>% # Group by interval
  summarize(atp_x = mean(rank == 1))%>%
  pull(atp_x)
```

```{r}
df_summary$lymph_no_x <- lymph_cmp %>%
  mutate(
    interval = cut(hi_score, breaks = seq(0, 1, length.out = 21), include.lowest = TRUE) # Create intervals
  ) %>%
  group_by(interval) %>% # Group by interval
  summarize(lymph_no_x = mean(rank == 1))%>%
  pull(lymph_no_x)
```

```{r}
df_summary$lymph_x <-lymph_cmp_crosswalk %>%
  mutate(
    interval = cut(hi_score, breaks = seq(0, 1, length.out = 21), include.lowest = TRUE) # Create intervals
  ) %>%
  group_by(interval) %>% # Group by interval
  summarize(lymph_x = mean(rank == 1))%>%
  pull(lymph_x)
```

```{r}
df_summary$usr_no_x_2 <-usr_cmp_soc2 %>%
  mutate(
    interval = cut(hi_score, breaks = seq(0, 1, length.out = 21), include.lowest = TRUE) # Create intervals
  ) %>%
  group_by(interval) %>% # Group by interval
  summarize(usr_no_x_2 = mean(rank == 1))%>%
  pull(usr_no_x_2)
```

```{r}
df_summary$atp_no_x_2 <-atp_cmp_soc2 %>%
  mutate(
    interval = cut(hi_score, breaks = seq(0, 1, length.out = 21), include.lowest = TRUE) # Create intervals
  ) %>%
  group_by(interval) %>% # Group by interval
  summarize(atp_no_x_2 = mean(rank == 1))%>%
  pull(atp_no_x_2)
```

```{r}
df_summary$lymph_no_x_2 <-lymph_cmp_soc2 %>%
  mutate(
    interval = cut(hi_score, breaks = seq(0, 1, length.out = 21), include.lowest = TRUE) # Create intervals
  ) %>%
  group_by(interval) %>% # Group by interval
  summarize(lymph_no_x_2 = mean(rank == 1))%>%
  pull(lymph_no_x_2)
```

```{r}
df_summary1 = df_summary
df_summary1$start_value = df_summary1%>%
  mutate(start_value = as.numeric(sub("\\((.+),.+\\]", "\\1", as.character(interval))))%>%
  pull(start_value)
df_summary1$start_value[1]=0
```


```{r}
ggplot(df_summary1)+
  geom_point(aes(x = start_value, y = usr_no_x), shape = 1)+
  geom_point(aes(x = start_value, y = usr_x), shape = 19)+
  geom_point(aes(x = start_value, y = atp_no_x), shape = 2)+
  geom_point(aes(x = start_value, y = atp_x), shape = 17)+
  geom_point(aes(x = start_value, y = lymph_no_x), shape = 0)+
  geom_point(aes(x = start_value, y = lymph_x), shape = 15)+
  scale_x_continuous(
    name = "Interval Start", 
    breaks = seq(0,1, by = .05)
  ) 
```
```{r}
df_long <- df_summary[, 1:7] %>%
  pivot_longer(
    cols = -c(interval),               # Columns to pivot (all except 'interval')
    names_to = "group",             # New column for variable names
    values_to = "value"             # New column for values
  ) %>%
  mutate(
    facet_group = case_when(        # Create a grouping variable for faceting
      grepl("usr", group) ~ "USR",
      grepl("atp", group) ~ "ATP",
      grepl("lymph", group) ~ "Asia Lymph"
    ),
    shape = case_when(              # Assign shapes based on suffix
      grepl("_no_x$", group) ~ 17,  # Triangle shape for groups ending in '_no_x'
      grepl("_x$", group) ~ 19      # Circle shape for groups ending in '_x'
    ),
    start_value = as.numeric(sub("\\((.+),.+\\]", "\\1", as.character(interval))))

df_long$start_value[1:6] = 0

# Plot with faceting
ggplot(df_long, aes(x = start_value, y = value, shape = factor(shape))) +
  geom_point(size = 2) +
  geom_smooth(method = "lm", aes(linetype = factor(shape)), se= FALSE)+
  facet_wrap(~facet_group, scales = "free_y") +  # Create separate subplots
  scale_shape_manual(values = c(17, 19), labels = c("Without Crosswalk", "With Crosswalk")) + # Map shapes+
  scale_linetype_manual(values = c(17, 19), labels = c("Without Crosswalk", "With Crosswalk"))+
  scale_x_continuous(
    name = "Soccer Score (In Intervals)", 
    breaks = seq(0,1, by = .10)
  ) +
  scale_y_continuous(0, 1, breaks = seq(0,1, by = .10), name = "Percent Agreement")+
  labs(
    shape = "Group Type",
    linetype = "Group Type"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5)) # Rotate x-axis labels for readability
```
```{r}
df_summary$center = df_summary %>%
  mutate(
    # Extract start and end of intervals using regex
    start = as.numeric(sub("\\(([^,]+),.*", "\\1", as.character(interval))),  # Extract start
    center = start +.025
  )%>%
  pull(center)
df_summary$center[1]= .025
```


```{r}
df_summary_nox = df_summary[, c(11, 2,4,6, 8, 9, 10)] 
```

```{r}
df_summary_x = df_summary[,c(11, 3,5,7)]
```

```{r}
df_long_nox = df_summary_nox %>%
  pivot_longer(
    cols = -center,                 # Columns to pivot (all except 'center')
    names_to = "group",             # New column for variable names
    values_to = "value"             # New column for values
  ) %>%
  mutate(
    facet_group = case_when(        # Create a grouping variable for faceting
      grepl("usr_no_x", group) ~ "USR",
      grepl("atp_no_x", group) ~ "ATP",
      grepl("lymph", group) ~ "Asia Lymph"
    )) %>%
  mutate(
    facet_shape = case_when(
      grepl("no_x_2", group) ~ "Soccer 2.0",
      grepl("no_x", group) ~ "Soccer Net",
    )
  )

ggplot(df_long_nox, aes(x = center, y = value, color = facet_group, shape = facet_shape)) +
  geom_point() +
  geom_smooth(aes(linetype = facet_shape), method = "lm", se = FALSE) +
  labs(
    x = "Highest Model Score",
    y = "Percent Agreement",
    color = "Study",
    shape = "Model Type",
    linetype = "Model Type",
    title = "Score vs. Agreement without Crosswalk"
  ) +
  ylim(0, 1)  # Correct syntax for setting y-axis limits

```

```{r}
df_long_x = df_summary_x %>%
  pivot_longer(
    cols = -center,                 # Columns to pivot (all except 'center')
    names_to = "group",             # New column for variable names
    values_to = "value"             # New column for values
  ) %>%
  mutate(
    facet_group = case_when(        # Create a grouping variable for faceting
      grepl("usr", group) ~ "USR",
      grepl("atp", group) ~ "ATP",
      grepl("lymph", group) ~ "Asia Lymph"
    )
  )

ggplot(df_long_x, aes(x = center, y = value, color = facet_group)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(
    x = "Highest Model Score",
    y = "Percent Agreement",
    color = "Study",
    title = "Score vs. Agreement with Crosswalk"
  ) +
  ylim(0, 1)  # Correct syntax for setting y-axis limits

```

```{r}
ranks_df = data.frame(1,2,3,4,5,6,7,8,9,10,11)
```

```{r}
ranks_df[1,] <- usr_cmp %>%
  summarize(
    !!!setNames(
      lapply(1:max(.$rank, na.rm = TRUE), function(i) mean(.$rank <= i, na.rm = TRUE)),
      paste0("pct_", 1:max(.$rank, na.rm = TRUE))
    )
  )
```

```{r}
ranks_df[2,] <- usr_cmp_crosswalk %>%
  summarize(
    !!!setNames(
      lapply(1:max(.$rank, na.rm = TRUE), function(i) mean(.$rank <= i, na.rm = TRUE)),
      paste0("pct_", 1:max(.$rank, na.rm = TRUE))
    )
  )
```

```{r}
ranks_df[3,] <- atp_cmp %>%
  summarize(
    !!!setNames(
      lapply(1:max(.$rank, na.rm = TRUE), function(i) mean(.$rank <= i, na.rm = TRUE)),
      paste0("pct_", 1:max(.$rank, na.rm = TRUE))
    )
  )
```

```{r}
ranks_df[4,] <- atp_cmp_crosswalk %>%
  summarize(
    !!!setNames(
      lapply(1:max(.$rank, na.rm = TRUE), function(i) mean(.$rank <= i, na.rm = TRUE)),
      paste0("pct_", 1:max(.$rank, na.rm = TRUE))
    )
  )
```

```{r}
ranks_df[5,] <- lymph_cmp %>%
  summarize(
    !!!setNames(
      lapply(1:max(.$rank, na.rm = TRUE), function(i) mean(.$rank <= i, na.rm = TRUE)),
      paste0("pct_", 1:max(.$rank, na.rm = TRUE))
    )
  )
```

```{r}
ranks_df[6,] <- lymph_cmp_crosswalk %>%
  summarize(
    !!!setNames(
      lapply(1:max(.$rank, na.rm = TRUE), function(i) mean(.$rank <= i, na.rm = TRUE)),
      paste0("pct_", 1:max(.$rank, na.rm = TRUE))
    )
  )
```

```{r}
rownames(ranks_df) = c("USR without Crosswalk", "USR with Crosswalk", "ATP without Crosswalk", "ATP with Crosswalk", "Asia Lymph without Crosswalk", "Asia Lymph with Crosswalk")
```

```{r}
ranks_df <- ranks_df %>%
  rownames_to_column(var = "study") # "study" will hold the old row names

long_df <- ranks_df %>%
  pivot_longer(
    cols = starts_with("X"),     # Select percentage columns
    names_to = "pct_rank",          # New column for the rank
    values_to = "cumulative_pct"    # New column for the cumulative percentage
  ) %>%
  mutate(
    pct_rank = as.numeric(gsub("X", "", pct_rank)) # Convert rank names to numeric
  )
```

```{r}
ggplot(long_df, aes(x = pct_rank, y = cumulative_pct, color = study, group = study)) +
  geom_line(size = 1) +
  geom_point(size = 2) +
  labs(
    x = "Rank of expert SOC",
    y = "Cumulative proportion of jobs",
    title = "Cumulative Percentages by Rank",
    color = "Study"
  ) +
  scale_x_continuous(breaks = 1:11) +
  scale_y_continuous(limits = c(0,1))+
  theme_minimal()
```
# Inputting Crosswalk Files and Creating Num_Crosswalk Columns
## Asia Lymph
```{r}
xwalk_lymph = read.csv('/Users/orszagl2/Documents/socR/crosswalk files/isco1988_soc2010.csv')
xwalk_lymph = xwalk(xwalk_lymph)
```

```{r}
lymph_crosswalk_tibble = as.tibble(lymph_crosswalk)
lymph_crosswalk_tibble = lymph_crosswalk_tibble %>% crosswalk_columns(xwalk_lymph, num_crosswalk, isco1988, unnest_results = TRUE)
lymph_crosswalk_num = as.data.frame(lymph_crosswalk_tibble)
lymph_crosswalk_num <- lymph_crosswalk_num %>%
  rowwise() %>%
  mutate(num_crosswalk_count = sum(!is.na(c_across(starts_with("num_crosswalk"))))) %>%
  ungroup()
```

### Combining Old and New Dataframes to Have Scores in 1 Dataframe
```{r}
lymph_full = inner_join(lymph_crosswalk_num, lymph_no_crosswalk, by = "Id")
```

### Graph
```{r}
ggplot(lymph_full, aes(y = score_1.x, x = score_1.y))+
  geom_point(aes(color = num_crosswalk_count))+
  labs(y = "Score with Crosswalk",
       x = "Score without Crosswalk",
       title = "Score with vs. without Crosswalk (Asia Lymph)",
       color = "# of Possible SOC Scores")
```

```{r}
ggplot(lymph_full)+
  geom_histogram(aes(x = num_crosswalk_count), binwidth = 1)+
  labs (x = "Number of Possible SOC Codes",
        y = "Count",
        title = "Histogram of # Of Possible SOC Codes \n from Original ISCO 1988 Codes (Asia Lymph)")
```
```{r}
lymph_full_grouped <- lymph_full %>%
  mutate(score_bins_xw = cut(
    score_1.x,
    breaks = seq(0, 1.00, by = 0.05),  # Breaks every 0.05, extending beyond 1
    include.lowest = TRUE,
    labels = paste0(
      seq(0, 0.95, by = 0.05),
      "-",
      seq(0.05, 1, by = 0.05)
    ))) %>%
    mutate(score_bins_no_xw = cut(
    score_1.y,
    breaks = seq(0, 1.00, by = 0.05),  # Breaks every 0.05, extending beyond 1
    include.lowest = TRUE,
    labels = paste0(
      seq(0, 0.95, by = 0.05),
      "-",
      seq(0.05, 1, by = 0.05)
    ))
  )
```

```{r}
ggplot(lymph_full_grouped)+
  geom_boxplot(aes(x = score_bins_xw, y = num_crosswalk_count))+
  labs (x = "Score, Grouped (With Crosswalk)",
        y = "Number of SOC Scores",
        title = "Number of SOC Scores Possible from ISCO Score \n per Score Range (Asia Lymph)")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

```{r}
# this graph looks at the number of possible soc scores from the crosswalk and compares it to the corresponding NON-crosswalked score
ggplot(lymph_full_grouped)+
  geom_boxplot(aes(x = score_bins_no_xw, y = num_crosswalk_count))+
  labs (x = "Score, Grouped (Without Crosswalk)",
        y = "Number of SOC Scores",
        title = "Number of SOC Scores Possible from ISCO Score \n per Score Range (Asia Lymph)")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

## ATP
```{r}
xwalk_atp = read.csv('/Users/orszagl2/Documents/socR/crosswalk files/noc2011_soc2010_via_soc2018.csv')
xwalk_atp = xwalk(xwalk_atp)
```

```{r}
atp_crosswalk_tibble = as.tibble(atp_crosswalk)
atp_crosswalk_tibble = atp_crosswalk_tibble %>% crosswalk_columns(xwalk_atp, num_crosswalk, noc2011, unnest_results = TRUE)
atp_crosswalk_num = as.data.frame(atp_crosswalk_tibble)
atp_crosswalk_num <- atp_crosswalk_num %>%
  rowwise() %>%
  mutate(num_crosswalk_count = sum(!is.na(c_across(starts_with("num_crosswalk"))))) %>%
  ungroup()
```

### Combining Old and New Dataframes to Have Scores in 1 Dataframe
```{r}
atp_full = inner_join(atp_crosswalk_num, atp_no_crosswalk, by = "Id")
```

### Graph
```{r}
ggplot(atp_full, aes(y = score_1.x, x = score_1.y))+
  geom_point(aes(color = num_crosswalk_count))+
  labs(y = "Score with Crosswalk",
       x = "Score without Crosswalk",
       title = "Score with vs. without Crosswalk (ATP)",
       color = "# of Possible SOC Scores")
```

```{r}
ggplot(atp_full)+
  geom_histogram(aes(x = num_crosswalk_count), binwidth = 1)+
  labs (x = "Number of Possible SOC Codes",
        y = "Count",
        title = "Histogram of # Of Possible SOC Codes \nfrom original NOC Code (ATP)")
```

```{r}
atp_full_grouped <- atp_full %>%
  mutate(score_bins_xw = cut(
    score_1.x,
    breaks = seq(0, 1.00, by = 0.05),  # Breaks every 0.05, extending beyond 1
    include.lowest = TRUE,
    labels = paste0(
      seq(0, 0.95, by = 0.05),
      "-",
      seq(0.05, 1, by = 0.05)
    ))) %>%
    mutate(score_bins_no_xw = cut(
    score_1.y,
    breaks = seq(0, 1.00, by = 0.05),  # Breaks every 0.05, extending beyond 1
    include.lowest = TRUE,
    labels = paste0(
      seq(0, 0.95, by = 0.05),
      "-",
      seq(0.05, 1, by = 0.05)
    ))
  )
```

```{r}
ggplot(atp_full_grouped)+
  geom_boxplot(aes(x = score_bins_xw, y = num_crosswalk_count))+
  labs (x = "Score, Grouped (With Crosswalk)",
        y = "Number of SOC Scores",
        title = "Number of Possible SOC Scores from NOC Code \nper Score Range (ATP)")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

```{r}
ggplot(atp_full_grouped)+
  geom_boxplot(aes(x = score_bins_no_xw, y = num_crosswalk_count))+
  labs (x = "Score, Grouped (Without Crosswalk)",
        y = "Number of SOC Scores",
        title = "Number of Possible SOC Scores from NOC Code \nper Score Range (ATP)")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

## USR
```{r}
xwalk_usr = read.csv('/Users/orszagl2/Documents/socR/crosswalk files/soc1980_soc2010.csv')
xwalk_usr = xwalk(xwalk_usr)
```

```{r}
usr_crosswalk_tibble = as.tibble(usr_crosswalk)
usr_crosswalk_tibble = usr_crosswalk_tibble %>% crosswalk_columns(xwalk_usr, num_crosswalk, soc1980, unnest_results = TRUE)
usr_crosswalk_num = as.data.frame(usr_crosswalk_tibble)
usr_crosswalk_num <- usr_crosswalk_num %>%
  rowwise() %>%
  mutate(num_crosswalk_count = sum(!is.na(c_across(starts_with("num_crosswalk"))))) %>%
  ungroup()
```

### Combining Old and New Dataframes to Have Scores in 1 Dataframe
```{r}
usr_full = inner_join(usr_crosswalk_num, usr_no_crosswalk, by = "Id")
```

### Graph
```{r}
ggplot(usr_full, aes(y = score_1.x, x = score_1.y))+
  geom_point(aes(color = num_crosswalk_count))+
  labs(y = "Score with Crosswalk",
       x = "Score without Crosswalk",
       title = "Score with vs. without Crosswalk (USR)",
       color = "# of Possible SOC Scores")
```

```{r}
ggplot(usr_full)+
  geom_histogram(aes(x = num_crosswalk_count), binwidth = 1)+
  labs (x = "Number of Possible SOC Codes",
        y = "Count",
        title = "Histogram of # Of Possible SOC Codes from \n1980 SOC Code (USR)")
```

```{r}
usr_full_grouped <- usr_full %>%
  mutate(score_bins_xw = cut(
    score_1.x,
    breaks = seq(0, 1.00, by = 0.05),  # Breaks every 0.05, extending beyond 1
    include.lowest = TRUE,
    labels = paste0(
      seq(0, 0.95, by = 0.05),
      "-",
      seq(0.05, 1, by = 0.05)
    ))) %>%
    mutate(score_bins_no_xw = cut(
    score_1.y,
    breaks = seq(0, 1.00, by = 0.05),  # Breaks every 0.05, extending beyond 1
    include.lowest = TRUE,
    labels = paste0(
      seq(0, 0.95, by = 0.05),
      "-",
      seq(0.05, 1, by = 0.05)
    ))
  )
```

```{r}
ggplot(usr_full_grouped)+
  geom_boxplot(aes(x = score_bins_xw, y = num_crosswalk_count))+
  labs (x = "Score, Grouped (With Crosswalk)",
        y = "Number of SOC Scores",
        title = "Number of Possible SOC Scores from SOC 1980 Code \nper Score Range (USR)")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

```{r}
ggplot(usr_full_grouped)+
  geom_boxplot(aes(x = score_bins_no_xw, y = num_crosswalk_count))+
  labs (x = "Score, Grouped (Without Crosswalk)",
        y = "Number of SOC Scores",
        title = "Number of Possible SOC Scores from SOC 1980 Code \nper Score Range (USR)")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

# Percent of Jobs Where Expert Code was Chosen
## Lymph
```{r}
lymph_cmp%>%
  mutate(is_present = map2_lgl(soc2010_coder, soc2010_soccer, ~ any(.x %in% .y)))%>%
  summarize(mean(is_present))

lymph_cmp_crosswalk%>%
  mutate(is_present = map2_lgl(soc2010_coder, soc2010_soccer, ~any(.x %in% .y)))%>%
  summarize(mean(is_present))
```
## ATP
```{r}
atp_cmp%>%
  mutate(is_present = map2_lgl(soc2010_coder, soc2010_soccer, ~any(.x %in% .y)))%>%
  summarize(mean(is_present))

atp_cmp_crosswalk%>%
  mutate(is_present = map2_lgl(soc2010_coder, soc2010_soccer, ~any(.x %in% .y)))%>%
  summarize(mean(is_present))
```
## USR
```{r}
usr_cmp%>%
  mutate(is_present = map2_lgl(soc2010_coder, soc2010_soccer, ~any(.x %in% .y)))%>%
  summarize(mean(is_present))

usr_cmp_crosswalk%>%
  mutate(is_present = map2_lgl(soc2010_coder, soc2010_soccer, ~any(.x %in% .y)))%>%
  summarize(mean(is_present))
```

## Create Table
```{r}
percent_df = data.frame (row.names = c("Asia Lymph", "ATP", "USR"))
```

```{r}
percent_df[1, 1] = .786
percent_df[1, 2] = .810
percent_df[2, 1] = .919
percent_df[2, 2] = .930
percent_df[3, 1] = .882
percent_df[3, 2] = .927
colnames(percent_df) = c("Without Crosswalk", "With Crosswalk")
```

```{r}
kable(percent_df, caption = "Percent of Cases for Which Expert Code is Included in SOC Output")
```

# Difference in Xwalk vs. Non Xwalk Scores
## 
```{r}
usr_full$score_diff = usr_full$score_1.x - usr_full$score_1.y
atp_full$score_diff = atp_full$score_1.x - atp_full$score_1.y
lymph_full$score_diff = lymph_full$score_1.x - lymph_full$score_1.y
```

```{r}
ggplot(usr_full)+
  geom_histogram(aes(x = score_diff), binwidth = .05)+
  labs( y = "Count",
        x = "Score Difference \n (Crosswalk Score 1 - No Crosswalk Score 1)",
        title = "USR Score Differences")+
  scale_x_continuous(n.breaks = 10)+
  theme_minimal()
```
```{r}
ggplot(atp_full)+
  geom_histogram(aes(x = score_diff), binwidth = .05)+
  labs( y = "Count",
        x = "Score Difference \n (Crosswalk Score 1 - No Crosswalk Score 1)",
        title = "ATP Score Differences")+
  scale_x_continuous(n.breaks = 10)+
  theme_minimal()
```
```{r}
ggplot(lymph_full)+
  geom_histogram(aes(x = score_diff), binwidth = .05)+
  labs( y = "Count",
        x = "Score Difference \n (Crosswalk Score 1 - No Crosswalk Score 1)",
        title = "Asia Lymph Score Differences")+
  scale_x_continuous(n.breaks = 10)+
  theme_minimal()
```

# 1 to 1 Agreement Graphs
## USR
### Data
```{r}
usr_cmp$source = rep("No Crosswalk", 11943)
usr_cmp_crosswalk$source = rep("Crosswalk", 11943)
usr_agreement = rbind(usr_cmp, select(usr_cmp_crosswalk, -soc1980))
usr_agreement$agree = ifelse(usr_agreement$rank == 1, "Agree", "Disagree")
```

### Graphs
```{r}
ggplot(usr_agreement, aes(x = hi_score))+
  geom_histogram(binwidth = .05, fill = "cornflowerblue")+
  facet_wrap(agree ~ source)+
  labs (x = "Highest Soccer Score",
        y = "Count",
        title = "USR Soccer Scores, by Crosswalk & Agreement with Expert Codes")
```
## ATP
### Data
```{r}
atp_cmp$source = rep("No Crosswalk", 446)
atp_cmp_crosswalk$source = rep("Crosswalk", 446)
colnames(atp_cmp)[4] = "noc2011"
atp_agreement = rbind(atp_cmp, atp_cmp_crosswalk)
atp_agreement$agree = ifelse(atp_agreement$rank == 1, "Agree", "Disagree")
```

### Graphs
```{r}
ggplot(atp_agreement, aes(x = hi_score))+
  geom_histogram(binwidth = .05, fill = "purple4")+
  facet_wrap(agree ~ source)+
  labs (x = "Highest Soccer Score",
        y = "Count",
        title = "ATP Soccer Scores, by Crosswalk & Agreement with Expert Codes")
```
## Lymph
### Data
```{r}
lymph_cmp$source = rep("No Crosswalk", 1496)
lymph_cmp_crosswalk$source = rep("Crosswalk", 1496)
colnames(lymph_cmp)[4] = "isco1988"
lymph_agreement = rbind(lymph_cmp, lymph_cmp_crosswalk)
lymph_agreement$agree = ifelse(lymph_agreement$rank == 1, "Agree", "Disagree")
```

### Graphs
```{r}
ggplot(lymph_agreement, aes(x = hi_score))+
  geom_histogram(binwidth = .05, fill = "turquoise4")+
  facet_wrap(agree ~ source)+
  labs (x = "Highest Soccer Score",
        y = "Count",
        title = "Asia Lymph Soccer Scores, by Crosswalk & Agreement with Expert Codes")
```

## USR
```{r}
usr_full_new = inner_join(usr_cmp_crosswalk, usr_no_crosswalk, by = "Id")
usr_full_new$score_diff = usr_full_new$hi_score - usr_full_new$score_1
```

```{r}
usr_full_new <- usr_full_new %>%
  mutate(score_bin_diff = factor(case_when(
    score_diff > 0.2  ~ "++",
    score_diff > 0.05 & score_diff <= 0.2  ~ "+",
    score_diff > -0.05 & score_diff <= 0.05  ~ "No change",
    score_diff > -0.2 & score_diff <= -0.05 ~ "-",
    TRUE ~ "--"
  ), levels = c("--", "-", "No change", "+", "++")))
```

```{r}
usr_summary <- usr_full_new %>%
  mutate(
    interval = cut(hi_score, breaks = seq(0, 1, length.out = 21), include.lowest = TRUE) # Create intervals
  ) %>%
  group_by(interval, score_bin_diff) %>% # Group by interval
  summarize(usr = mean(rank == 1))
```

```{r}
supp.labs = c(
  "Change greater than -.20",
  "Change between -.20 and -.05",
  "Change between -.05 and .05",
  "Change between .05 and .20",
  "Change greater than .20"
)
names(supp.labs) = c("--", "-", "No change", "+", "++")
```

```{r}
ggplot(usr_summary, aes(x = interval, y = usr))+
  geom_point()+
  facet_wrap(~score_bin_diff, labeller = labeller(score_bin_diff = supp.labs))+
  geom_smooth(aes(group = score_bin_diff), method = 'lm', color = "cornflowerblue", se = FALSE)+
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))+
  labs (x = "Highest Soccer Score with Crosswalk", 
        y = "Percent Agreement with Expert Code",
        title = "USR Highest Soccer Score vs. Pct Agreement, Stratified by Score Change")
```

## ATP
```{r}
atp_full_new = inner_join(atp_cmp_crosswalk, atp_no_crosswalk, by = "Id")
atp_full_new$score_diff = atp_full_new$hi_score - atp_full_new$score_1
```

```{r}
atp_full_new <- atp_full_new %>%
  mutate(score_bin_diff = factor(case_when(
    score_diff > 0.2  ~ "++",
    score_diff > 0.05 & score_diff <= 0.2  ~ "+",
    score_diff > -0.05 & score_diff <= 0.05  ~ "No change",
    score_diff > -0.2 & score_diff <= -0.05 ~ "-",
    TRUE ~ "--"
  ), levels = c("--", "-", "No change", "+", "++")))
```

```{r}
atp_summary <- atp_full_new %>%
  mutate(
    interval = cut(hi_score, breaks = seq(0, 1, length.out = 21), include.lowest = TRUE) # Create intervals
  ) %>%
  group_by(interval, score_bin_diff) %>% # Group by interval
  summarize(atp = mean(rank == 1))
```

```{r}
ggplot(atp_summary, aes(x = interval, y = atp))+
  geom_point()+
  facet_wrap(~score_bin_diff, labeller = labeller(score_bin_diff = supp.labs))+
  geom_smooth(aes(group = score_bin_diff), method = 'lm', color = "purple3", se = FALSE)+
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))+
  labs (x = "Highest Soccer Score with Crosswalk", 
        y = "Percent Agreement with Expert Code",
        title = "ATP Highest Soccer Score vs. Pct Agreement, Stratified by Score Change")
```


## Lymph
```{r}
lymph_full_new = inner_join(lymph_cmp_crosswalk, lymph_no_crosswalk, by = "Id")
lymph_full_new$score_diff = lymph_full_new$hi_score - lymph_full_new$score_1
```

```{r}
lymph_full_new <- lymph_full_new %>%
  mutate(score_bin_diff = factor(case_when(
    score_diff > 0.2  ~ "++",
    score_diff > 0.05 & score_diff <= 0.2  ~ "+",
    score_diff > -0.05 & score_diff <= 0.05  ~ "No change",
    score_diff > -0.2 & score_diff <= -0.05 ~ "-",
    TRUE ~ "--"
  ), levels = c("--", "-", "No change", "+", "++")))
```

```{r}
lymph_summary <- lymph_full_new %>%
  mutate(
    interval = cut(hi_score, breaks = seq(0, 1, length.out = 21), include.lowest = TRUE) # Create intervals
  ) %>%
  group_by(interval, score_bin_diff) %>% # Group by interval
  summarize(lymph = mean(rank == 1))
```

```{r}
ggplot(lymph_summary, aes(x = interval, y = lymph))+
  geom_point()+
  facet_wrap(~score_bin_diff, labeller = labeller(score_bin_diff = supp.labs))+
  geom_smooth(aes(group = score_bin_diff), method = 'lm', color = "turquoise4", se = FALSE)+
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))+
  labs (x = "Highest Soccer Score with Crosswalk", 
        y = "Percent Agreement with Expert Code",
        title = "Lymph Highest Soccer Score vs. Pct Agreement, Stratified by Score Change")
```